### 2016-06-28 appendix.tex
Need to add three more experiments
Three more charts
A complete version
An almost complete version
Near Done

\subsection{Proof of Theorem~\ref{THM:SPM_LB}}
\begin{proof}
We formalize optimization of $\Gamma$ using a linear algebra model as follows:  
Let $G_A$ be an aggregate graph, with a $n \times n$ adjacent matrix $J$.
A vertex order is in fact a permutation of $J$. Therefore,
the adjacent matrices of any reordered graphs can be represented as $PJP^T$
where $P \in \mathbb{P}$ is a 
\emph{permutation matrix}~\footnote{an identity matrix with rows shuffled} with dimension $n$.
Since in star partition, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
then the matrix $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
represents the assignment matrix wrt. $P$ (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
Let vector $\vec{b}$ be the \textit{one}\footnote{every element in $\vec{b}$ is $1$} 
vector of size $n$. Let $\vec{c} = B\vec{b}$, then each $c_i$ 
denotes the number of edges in star $Sr_i$. Thus, $\Gamma$ can be represented
as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orders. 
$\Gamma^*$ can then be formulated as follows:
\begin{equation}
\Gamma^* = \min_{P \in \mathbb{P}}{||B\vec{b}||_\infty} \text{ ,where } ||B\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
\end{equation}

Let $B*$ be the assignment matrix wrt the optimal vertex order.
Since we have a star for each object, by the degree-sum formula and pigeon-hole theorem, 
$\Gamma^*=||B^*\vec{b}||_\infty \geq d/2$.
Next, given a numbering $P$, let $e_{i,j}$ be an entry in $PAP^T$. Since 
edges in graph $G$ are independent, then $e_{i,j}$s are independent. Moreover,
let $d_i$ denote the degree of vertex $i$, 
then $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$. This is because renumbering the
vertexes does not affect the average degree.
Since $B=\text{triu}(PAP^T)$, entries in $B$ can be written as :
\begin{equation*}
b_{i,j} = \begin{cases}
			e_{i,j}, i>j \\
			0, otherwise
		  \end{cases}  
\end{equation*}
There are two observations made. First, since $e_{i,j}$s are independent,
$b_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$s are independent. 
$E[b_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.

By definition, $c_i = \Sigma_{1\leq j \leq n} b_{i,j}$, 
is a sum of $n$ independent 0-1 variables. Taking expectation on both sides, 
we get: $E[c_i] = E[\Sigma_{1\leq j \leq n} b_{i,j}]=E[\Sigma_{1\leq j \leq n} e_{i,j}]/2 = d/2$.
 Let $\mu =E[c_i] = d/2$, 
$t = \sqrt{n\log n}$, by Hoeffding's Inequality, the following holds:
\begin{equation*}
\begin{split}
	Pr(c_i \geq \mu + t) 
						&\leq \exp(\frac{-2t^2}{n}) \\
						&= \exp(-2\log n) = n^{-2}
\end{split}
\end{equation*}

The first step is due to the fact that all $b_{i,j}$ are bounded in the range of [0,1]. 
Next, since the event $(\max_{1 \leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
$\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, we achieve the following:
\begin{equation*}
\begin{split}
	Pr(\Gamma \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t)  \\
		& = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) \\
		& = n^{-1} = 1/n
\end{split}
\end{equation*}
Substitute back $t$ and $\mu$, we achieve the following concise form:
\begin{equation*}
	Pr(\Gamma \geq (d/2 + \sqrt{n\log n})) \leq 1/n
\end{equation*}
This indicates that, the probability of $(\Gamma-d/2)$ being less than or equal to $ O(\sqrt{n\log n})$ is $(1-1/n)$. 
With the fact that $\Gamma^* \geq d/2$, we conclude that
with probability greater than $(1-1/n)$, 
the difference between $\Gamma$ and $\Gamma^*$ is less than $O(\sqrt{n\log n})$.
When the aggregated graph is \emph{dense} (i.e., $d\geq \sqrt{12 \log n}$), we may use
the Chernoff Bound instead of Hoeffding's Inequality to derive a tighter bound of 
$O(\sqrt{\log n}) $ with the similar reasoning.
\end{proof}

@@

\subsection{Proof of Theorem~\ref{THM:SPM_CORRECT}}
\begin{proof}
For soundness, let $P$ be a pattern enumerated by SPARE. Since the enumerate algorithm only reduces the time sequences, for any two objects $o_1, o_2 \in P.O$, the edge $e(o_1,o_2)$ is a superset of $P.T$. By the definition of star, $\forall t \in T, C_t(o_1) = C_t(o_2)$. As $T$ is a valid sequence, by the definition of GCMP, $P$ is a true pattern.
For completeness, let $P$ is a true pattern. Let $s$ be the object with smallest ID in $P.O$. We prove that $P$ must be output by Algorithm~\ref{algo:apriori_mining} with input $Sr_s$. 
First, based on the definition of star, every object in $P.O$ appears in $Sr_s$. Since $P.T$ is decomposable, then $\forall O' \subseteq O$, the time sequence of $O'$ is a super set of a decomposable sequence. This indicates that $O'$ would not be eliminated by any $\mathtt{sim}$ operations in Algorithm~\ref{algo:apriori_mining}.  Next, we prove at every iteration \emph{level} $\leq |P.O|$, $P.O \subset O_u$, where $O_u$ is the forward closure. We prove by induction. When $level$ = 2, it obviously holds. If $P.O \subset O_u$ at \emph{level=$i$}, then any subset of $P.O$ with size $i$ are in the candidate set. In \emph{level} $i+1$, these subsets are able to grow to a bigger subset (in last iteration, they grow to $P.O$). This suggests that no subsets are removed by Lines~\ref{code:output1-start}-\ref{code:output2-end}. Then, $P.O \subset U_{i+1}$ holds. In summary, $P.O$ does not pruned by simplification, monotonicity and forward closure, therefore $P$ must be returned by SPARE.
%Next, observe that at each iteration $i$, candidates with size $i+2$ are generated. Then, $P.O$'s subset with size $i+2$ are always included in the candidate set at iteration $i$. This indicates that $O' \subset U$, thus any $O'$  would not be pruned by forward closure checking. Since none of the pruning operations removed $O'$, $P$ can be returned by SPARE.
%
%\begin{theorem}[Forward Closure Checking]
%\label{THM:SPM_FCC}
%Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining},
%if $FC_i$ is a proper pattern, then it is safe to terminate Algorithm~\ref{algo:apriori_mining}
%and directly output $FC_i$.
%\end{theorem}

%
%If $P$ is a valid pattern in original trajectories, 
%let $s$ be the object with smallest ID in $P.O$. 
%Based on the definition of GCMP, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
%It follows that all object $o \in P.O$ are in $Sr_s$. 
%Furthermore, every timestamp in $P.T$ is included
%in $Sr_s$. Therefore, $P$ is a valid pattern in $Sr_s$. This ensures the \emph{completeness}. For any pattern $P$ enumerated by SPARE, by definition of star partition, $\forall o_1, o_2 \in P.O$, $\forall t \in P.T$, $C_t(o_1) = C_t(o_2)$. This ensure the \emph{soundness}.
\end{proof}

%\subsection{Proof of Theorem~\ref{THM:SPM_FCC}}
%\begin{proof}
%We prove by contradiction. Suppose there exists another pattern $P$ such that $P.O \neq FC_i$, 
%let $X=P.O - FC_i \neq \emptyset$. Consider a subset $P_1$ of $P$ which contains $X$ with size $i+1$, 
%(i.e., $P_1 \subseteq P, P_1\subseteq X, |P_1|=i+1$). Since $P$ is a proper pattern, 
%then $P_1$ is also a proper pattern. Therefore $P_1 \in Lv_i$.
%It follows $X$ is in the forward closure of $FC_i$, (i.e.,$X \in FC_i$), which contradicts with $X\notin FC_i$.
%\end{proof}

>>>>

\subsection{Proof of Theorem~\ref{THM:SPM_LB} and~\ref{THM:SPM_LB_INC}}
\label{apx:thm2proof}
\begin{proof}
$\Gamma$ can be formalized in a linear algebra way:
Let $G_A$ be an aggregate graph, with a $n \times n$ adjacent matrix $J$.
Since a vertex order is a permutation of $J$, the adjacent matrices 
of any reordered graphs can be represented as $PJP^T$
where $P \in \mathbb{P}$ is a $n\times n$ \emph{permutation matrix}~\footnote{an identity matrix with rows shuffled}.
In star partition, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
then the matrix $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
represents the assignment matrix wrt. $P$ (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
Let vector $\vec{b}$ be the \textit{one}\footnote{every element in $\vec{b}$ is $1$} 
vector with size $n$. Let $\vec{c} = B\vec{b}$, then each $c_i$ 
denotes the number of edges in star $Sr_i$. Thus, $\Gamma$ can be represented
as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orders, that is

\begin{equation}
\Gamma^* = \min_{P \in \mathbb{P}}{||B\vec{b}||_\infty} \text{ ,where } ||B\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
\end{equation}

Let $B^*$ be the assignment matrix wrt. the optimal vertex order.
Since we have a star for each object, by the degree-sum formula and pigeon-hole theorem, 
$\Gamma^*=||B^*\vec{b}||_\infty \geq d/2$.
Next, for a ordering $P$, let $e_{i,j}$ be an entry in $PAP^T$. Since 
edges in graph $G$ are independent, then $e_{i,j}$s are independent. 
Let $d_i$ denote the degree of vertex $i$, since ordering of vertex does not
affect the average degree,
then $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$. Therefore, 
entries in $B$ can be written as :

\begin{equation*}
b_{i,j} = \begin{cases}
			e_{i,j}, i>j \\
			0, otherwise
		  \end{cases}  
\end{equation*}

There are two observations. First, since $e_{i,j}$s are independent,
$b_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$s are independent. 
$E[b_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.
As $c_i$ is a sum of $n$ independent 0-1 variables ($b_{i.j}$s). By linearity 
of expectations,
we get: $E[c_i] = E[\Sigma_{1\leq j \leq n} b_{i,j}]=E[\Sigma_{1\leq j \leq n} e_{i,j}]/2 = d/2$.
 Let $\mu =E[c_i] = d/2$, 
$t = \sqrt{n\log n}$, by Hoeffding's Inequality, the following holds:

\begin{equation*}
\begin{split}
	Pr(c_i \geq \mu + t) &\leq \exp(\frac{-2t^2}{n}) \\
	 & = \exp(-2\log n) = n^{-2}
\end{split}
\end{equation*}

The first step holds since all $b_{i,j}$ are 0-1 variables. 
Next, the event $(\max_{1 \leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
$\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, the following holds:
\begin{equation*}
\begin{split}
	Pr(\Gamma \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t)  \\
		& = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) \\ 
		&= n^{-1} = 1/n
\end{split}
\end{equation*}
Substitute back $t$ and $\mu$, we achieve the following concise form:
\begin{equation*}
	Pr(\Gamma \geq (d/2 + \sqrt{n\log n})) \leq 1/n
\end{equation*}
This indicates the probability of $(\Gamma-d/2)$ being no greater than $ O(\sqrt{n\log n})$ is $(1-1/n)$. 
Since $\Gamma^* \geq d/2$, it follows with probability greater than $(1-1/n)$, 
the $\Gamma - \Gamma^*$ is no greater than $O(\sqrt{n\log n})$.
When the aggregated graph is \emph{dense} (i.e., $d\geq \sqrt{12 \log n}$),
the Chernoff Bound can be used to derive a tighter bound of 
$O(\sqrt{\log n}) $ following the similar reasoning.
\end{proof}

@@

\subsection{Proof of Theorem~\ref{THM:SPM_CORRECT}}
\label{apx:spm_correct}
\begin{proof}
For soundness, let $P$ be a pattern enumerated by SPARE. Since the enumerate algorithm only reduces the time sequences, for any two objects $o_1, o_2 \in P.O$, the edge $e(o_1,o_2)$ is a superset of $P.T$. By the definition of star, $\forall t \in T, C_t(o_1) = C_t(o_2)$. As $T$ is a valid sequence, by the definition of GCMP, $P$ is a true pattern.
For completeness, let $P$ is a true pattern. Let $s$ be the object with smallest ID in $P.O$. We prove that $P$ must be output by Algorithm~\ref{algo:apriori_mining} with input $Sr_s$. 
First, based on the definition of star, every object in $P.O$ appears in $Sr_s$. Since $P.T$ is decomposable, then $\forall O' \subseteq O$, the time sequence of $O'$ is a super set of a decomposable sequence. This indicates that $O'$ would not be eliminated by any $\mathtt{sim}$ operations in Algorithm~\ref{algo:apriori_mining}.  Next, we prove at every iteration \emph{level} $\leq |P.O|$, $P.O \subset O_u$, where $O_u$ is the forward closure. We prove by induction. When $level$ = 2, it obviously holds. If $P.O \subset O_u$ at \emph{level=$i$}, then any subset of $P.O$ with size $i$ are in the candidate set. In \emph{level} $i+1$, these subsets are able to grow to a bigger subset (in last iteration, they grow to $P.O$). This suggests that no subsets are removed by Lines~\ref{code:output1-start}-\ref{code:output2-end}. Then, $P.O \subset U_{i+1}$ holds. In summary, $P.O$ does not pruned by simplification, monotonicity and forward closure, therefore $P$ must be returned by SPARE.
\end{proof}

### 2016-06-28 sec1_introduction.tex
A complete version
An almost complete version
Near Done

\begin{table} \scriptsize
\centering
\begin{tabular}{|c|c|c|c|}
\hline 
Patterns & {\tiny Proximity} & {\tiny Consecutiveness} & {\tiny Time Complexity}\\ 
\hline 
flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||\mathbb{T}|(M + log(|\mathbb{O}|))$ \\ 
\hline 
convoy~\cite{jeung2008convoy} & density-based &   global & $O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$\\ 
\hline 
swarm~\cite{li2010swarm} & density-based  & - & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$  \\ 
\hline 
group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|\mathbb{T}|)$ \\ 
\hline 
platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$\\ 
\hline 
\end{tabular} 
\caption{Constraints and complexity of co-movement patterns. The time complexity indicates the performance in the worst case, where $|\mathbb{O}|$ is the total number of objects and $|\mathbb{T}|$ is the number of descritized timestamps.}
\label{tbl:existing_co_patterns}
\end{table}

\begin{figure}[h]
\centering
\includegraphics[width=0.46\textwidth]{related_work.eps}
\caption{Trajectories and co-movement patterns; The example consists of six trajectories across six snapshots. Objects in spatial clusters are enclosed by dotted circles. $M$ is the minimum cluster cardinality; $K$ denotes the minimum number of snapshots for the occurrence of a spatial cluster; and $L$ denotes the minimum length for local consecutiveness.}
\label{fig:related_work}
\end{figure}

@@

%As can be seen, there are various co-movement patterns requested by different 
%applications and it is cumbersome to design a tailored solution for each type. 
%As pointed in \cite{li2015platoon, li2010swarm}, stringent temporal constraints (e.g., global consecutiveness on \emph{flock} and \emph{convoy}) may miss out many interesting patterns. However, we 
%further observe that pattern definitions with overly-relaxed temporal constraints (e.g., \emph{swarm}, \emph{group} and \emph{platoon}) lose the fine control of a pattern which lead to noisy results and unnecessary computations. We name this scenario as \emph{loose-connection} anomaly. To illustrate, as shown in Figure~\ref{fig:platoon_weakpoint}, the two objects $o_1, o_2$ form a \emph{platoon} pattern 
%$\{o_1,o_2:1,2,3,102,103,104\}$. However, the consecutive segments are $98$ timestamps apart, 
%making the co-moving behavior very loose.
%In reality, such an anomaly is likely induced by the periodic movements of unrelated objects 
%such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc.  Interestingly, none of the temporal-relaxed patterns (e.g., \emph{swarm}, \emph{group} and \emph{platoon}) are able to directly avoid such an anomaly.

%In addition, existing pattern definitions are not expressive enough and may miss 
%interesting patterns or return noisy results. We summarize 
%the two scenarios as \emph{missing-pattern} anomaly
%and \emph{loose-connection} anomaly.
%A \emph{missing-pattern} anomaly arises due to the stringent constraints on the pattern duration.
%As shown in Figure~\ref{fig:platoon_weakpoint} (a), if we set $K=4$, 
%neither \emph{flock}s nor \emph{convoy}s can be discovered. This is because
%$o_1$ is away from $o_2$ at timestamp $4$, which is likely caused by
%the traffic control or the clustering inaccuracy at time $4$. On the other hand,
%the \emph{loose-connection} anomaly occurs due to an over-relaxed constraint on 
%the duration. As shown in Figure~\ref{fig:platoon_weakpoint} (b),
%the two objects $o_1, o_2$ form a \emph{platoon} pattern 
%$\{o_1,o_2:1,2,3,102,103,104\}$. However, the consecutive segments are $98$ timestamps apart, 
%making the co-moving behavior very weak.
%In reality, such an anomaly is likely to be induced by the periodic movements of unrelated objects 
%such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc. 
%It is easy to see that none of the existing co-movement patterns are able to avoid these two anomalies.

\begin{figure}[h]
\center
\includegraphics[width=0.35\textwidth]{platoon_weakpoint.eps}
\caption{\emph{Loose-connection} anomaly. Even though $\langle o_1, o_2: 1,2,3,102,103,104 \rangle$ is considered as a valid \emph{platoon} pattern, it is highly probable that these two objects are not related as the two consecutive segments  are 98 timestamps apart. 
% in \emph{platoon}, \emph{swarm} and \emph{group} results.
}
\label{fig:platoon_weakpoint}
\end{figure}

%In current literature,
%users are unable to explicitly exclude the loosely-connected patterns even when those patterns are unwanted.
%
%
% we summarize two anomalies 
%The \emph{missing-pattern}~\cite{li2010swarm} anomaly arises due to the stringent constraints on the duration of a pattern. As shown in 
%Figure~\ref{fig:platoon_weakpoint} (a).  As we notice, object $o_1$ is temporally far from $o_2$ at timestamp $4$, which is likely to be
%the result of errors in interpretation of missing points, or $o_1$ faces traffic control at time $4$. Such an anomaly can
%be resolved by \emph{swarm} and \emph{platoon} due to a relaxed constraint on the duration. However, 
%\emph{swarm} and \emph{platoon}'s relaxations encompass a type of non-interesting patterns which is referred
%as \emph{loose-connection}~\cite{li2015platoon} anomaly. 
%
%
%%This is because that \emph{platoon} allows the timestamps in a pattern duration to be in arbitrary distance, making the object group loosely
%connected. For instance, patterns with duration $\{1,2,100,101\}$ could be a valid \emph{platoon}; however, the two timestamps $2,100$ are too far from each other.

%For instance, PUT THE FIGURE AND EXPLANATION HERE.

%\begin{figure}[h]
%\center
%\includegraphics[width=0.35\textwidth]{rw_perf_O.eps}
%\caption{Two anomalies in existing patterns. (a) \emph{Missing-pattern} anomaly
%in \emph{flock} and \emph{convoy}. When $K=4$, none of the two patterns can be discovered. (b) \emph{Loose-connection} anomaly in \emph{platoon} and \emph{swarm}. The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is included in platoon and swarm results.}
%\label{fig:platoon_weakpoint}
%\end{figure}

The other issue with existing methods is that they are built on top of centralized indexes which may not be scalable. Table~\ref{tbl:existing_co_patterns} shows their theoretical complexities in the worst cases and the largest real dataset ever evaluated in previous studies is up to million-scale points collected from hundreds of moving objects. In practice, the dataset is of much higher scale and the scalability of existing methods is left unknown. Thus, we conduct an experimental evaluation with $4000$ objects moving for $2500$ timestamps to examine the scalability. Results in Figure~\ref{fig:related_work_scalability} show that their performances degrade dramatically as the dataset scales up. For instance, the detection time of \emph{group} drops twenty times as the number of objects grows from \emph{1k} to \emph{4k}. Similarly,
the performance of \emph{swarm} drops over fifteen times as the number of snapshots grows from \emph{1k} to \emph{2.5k}.
These observations imply that existing methods are not scalable to support large-scale trajectory databases.

%It is easy to spot that none of the existing solutions are scalable to handle large-scale trajectories which include near billions of data points.
%In fact, as shown in Table~, the mining of co-movement patterns require high complexity. For instance, the
%complexities of \emph{swarm} and \emph{platoon} are already exponential. 
%Therefore, none of them can handle millions of trajectories efficiently. 
%CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_O.eps}
		\subcaption{$1k$ timestamps}
    \label{fig:fig1}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_T.eps}
         \subcaption{$1k$ objects}
    \label{fig:fig2}
    \end{subfigure}
    \caption{Performance measures on existing co-movement patterns. A sampled Geolife data set
    is used with up two 2.4 million data points. Default parameters are $M=15$ $K=180$ $L=30$.}
    \label{fig:related_work_scalability}
\end{figure}

@@

%Therefore, users are 
%still able to exclude non-consecutive patterns 
%or include loosely-connected patterns when they feel necessary.

%We introduce the gap parameter $G$,
%When such loosely-connected patterns are unwanted, users currently are unable to directly control the outputs.
%To cope with both of the two anomalies, we propose 
%by introducing the gap parameter $G$,

%By so doing, we gain a fine-grained control s, which As we show in later sections, the general co-movement pattern is able to express existing patterns by setting appropriate parameters. 
%IS IT POSSIBLE TO USE FIGURE 1 TO ADDRESS THE PROBLEM OF PLATOON, INSTEAD OF PROPOSING A NEW EXAMPLE SCENARIO?
%

Second, we investigate deploying our GCMP detector on MapReduce platforms (such as Hadoop and Spark) to tackle the scalability issue. Our technical contributions are three-fold. First, we replicate the snapshots in multiple data chunks to support efficient parallel processing. Second, we devise a novel \emph{Star Partition and ApRiori Enumerator} (SPARE) framework as a fine-granularity partitioning strategy to achieve workload balance. For each star, an Apriori Enumerator is adopted to mine the co-movement patterns. Third, we leverage the \emph{temporal monotonicity} property of of GCMP 
to design several optimization techniques including \emph{sequence simplification}, \emph{monontonicity pruning} and \emph{forward closure check} to further reduce the number of candidates enumerated.
%
%we propose two types of optimization techniques to further improve the performance, including \emph{edge-simplification} to boost the shuffle process and \emph{temporal monotonicity pruning} and 
%\emph{forward closure checking} to significantly reduce the number of enumerated candidates in the Aproiro algorithm.

@@

The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
trajectory pattern mining. Section~\ref{sec:definition} states the problem definition of our general co-movement pattern mining. Section~\ref{sec:trm} provides a baseline solution. An advanced solution named
\emph{star partition and mining} is presented in Section~\ref{sec:spm}. Section~\ref{sec:exp} conducts extensive experiments to verify the efficiency of our system. Finally Section~\ref{sec:concl} concludes the paper.

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{related_work.eps}
\caption{Trajectories and co-movement patterns; The example consists of six trajectories across six snapshots. Objects in spatial clusters are enclosed by dotted circles. $M$ is the minimum cluster cardinality; $K$ denotes the minimum number of snapshots for the occurrence of a spatial cluster; and $L$ denotes the minimum length for local consecutiveness.}
\label{fig:related_work}
\end{figure}

@@

\begin{figure}[h]
\center
\includegraphics[width=0.3\textwidth]{platoon_weakpoint.eps}
\caption{\emph{Loose-connection} anomaly. Even though $\langle o_1, o_2: 1,2,3,102,103,104 \rangle$ is considered as a valid \emph{platoon} pattern, it is highly probable that these two objects are not related as the two consecutive segments  are 98 timestamps apart. 
}
\label{fig:platoon_weakpoint}
\end{figure}

\begin{table} \scriptsize
\centering
\begin{tabular}{|c|c|c|c|}
\hline 
Patterns & {\tiny Proximity} & {\tiny Consecutiveness} & {\tiny Time Complexity}\\ 
\hline 
flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||\mathbb{T}|(M + log(|\mathbb{O}|))$ \\ 
\hline 
convoy~\cite{jeung2008convoy} & density-based &   global & $O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$\\ 
\hline 
swarm~\cite{li2010swarm} & density-based  & - & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$  \\ 
\hline 
group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|\mathbb{T}|)$ \\ 
\hline 
platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$\\ 
\hline 
\end{tabular} 
\caption{Constraints and complexity of co-movement patterns. The time complexity indicates the performance in the worst case, where $|\mathbb{O}|$ is the total number of objects and $|\mathbb{T}|$ is the number of descritized timestamps.}
\label{tbl:existing_co_patterns}
\end{table}
The other issue with existing methods is that they are built on top of centralized indexes which may not be scalable. Table~\ref{tbl:existing_co_patterns} shows their theoretical complexities in the worst cases and the largest real dataset ever evaluated in previous studies is up to million-scale points collected from hundreds of moving objects. In practice, the dataset is of much higher scale and the scalability of existing methods is left unknown. Thus, we conduct an experimental evaluation with $4000$ objects moving for $2500$ timestamps to examine the scalability. Results in Figure~\ref{fig:related_work_scalability} show that their performances degrade dramatically as the dataset scales up. For instance, the detection time of \emph{group} drops twenty times as the number of objects grows from \emph{1k} to \emph{4k}. Similarly,
the performance of \emph{swarm} drops over fifteen times as the number of snapshots grows from \emph{1k} to \emph{2.5k}.
These observations imply that existing methods are not scalable to support large-scale trajectory databases.

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_O.eps}
		\subcaption{$1k$ timestamps}
    \label{fig:fig1}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_T.eps}
         \subcaption{$1k$ objects}
    \label{fig:fig2}
    \end{subfigure}
    \caption{Performance measures on existing co-movement patterns. A sampled Geolife data set
    is used with up two 2.4 million data points. Default parameters are $M=15$ $K=180$ $L=30$.}
    \label{fig:related_work_scalability}
\end{figure}

@@

Second, we investigate deploying our GCMP detector on MapReduce platforms (such as Hadoop and Spark) to tackle the scalability issue. Our technical contributions are three-fold. First, we replicate the snapshots in multiple data chunks to support efficient parallel processing. Second, we devise a novel \emph{Star Partition and ApRiori Enumerator} (SPARE) framework as a fine-granularity partitioning strategy to achieve workload balance. For each star, an Apriori Enumerator is adopted to mine the co-movement patterns. Third, we leverage the \emph{temporal monotonicity} property of of GCMP 
to design several optimization techniques including \emph{sequence simplification}, \emph{monontonicity pruning} and \emph{forward closure check} to further reduce the number of candidates enumerated.

@@

The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
trajectory pattern mining. Section~\ref{sec:definition} states the problem definition of our general co-movement pattern mining. Section~\ref{sec:trm} provides a baseline solution. An advanced solution named
\emph{Star Partition and ApRiori Enumerator} (SPARE) is presented in Section~\ref{sec:spm}. Section~\ref{sec:exp} conducts extensive experiments to verify the efficiency of our system. Finally Section~\ref{sec:concl} concludes the paper.
